---
title: "Homework 1"
author: "Alex Tryforos"
date: "8/27/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#1, 2, & 3
```{r}
#1 Create vector of positive intgers less than (but not equal to) 100
(v1 = seq(from=1, to=99, by=2.0))
#2 Remove values greater than 60 and less than 80
(v2 = v1[v1<60 | v1>80])
#3 Find variance of v2
var(v2)
```

#4
```{r}
#4 Create a dataframe
cone = data.frame(R=c(2.27,1.98,1.69,1.88,1.64,2.14), H=c(8.28, 8.04, 9.06, 8.70, 7.58, 8.34))
#Append Volume
cone$V = pi*cone$R**2*cone$H/3
cone
```

#5
```{r}
#Find the intercept and slope
x = matrix(c(1,1,1,1,3.15, -0.55, -0.35, 0.16),4,2)
y = c(2.93, -0.35, -0.25, -0.12)

(mat=solve(t(x)%*%x)%*%t(x)%*%y)
x=as.data.frame(x)
lm(y~V2, data=x)
```

#6, 7, & 8
```{r}
#6 Installing/Loading Packages
library(MASS)
data(cats)
head(cats)

#7 tables for males and females
table(cats$Sex)

#8 Compare Mean and SD of bods weights for male and females
#females
mean(cats$Bwt[cats$Sex=="F"])
sd(cats$Bwt[cats$Sex=="F"])
#males
mean(cats$Bwt[cats$Sex=="M"])
sd(cats$Bwt[cats$Sex=="M"])
```

Mean bodyweight for females is 2.359 with a standard deviation of 0.273.
Mean bodyweight for males is 2.9 with a standard deviation of 0.467.

#9 & 10
```{r}
#9 Find the proportion of male and female cats whose body weights are over 2.5 kilograms
#females
nrow(subset(cats, Sex == "F" & Bwt>2.5))/nrow(subset(cats, Sex =="F"))
nrow(subset(cats, Sex == "M" & Bwt>2.5))/nrow(subset(cats, Sex =="M"))

#10
#Creating lists that consist only male and female cats
catsF = cats[cats$Sex=="F",]
catsM = cats[cats$Sex=="M",]

```
23.4 Percent of females are above 2.5 kilograms.
74.4 Percent of males are above 2.5 kilograms.



#Central Limit Theorem Exercise for Normal Distribution
n=3 from normal distribution
```{r}
#Normal Distribution with N=10,000
#n=3
normsamp <- rnorm(10000,mean = 10, sd=5)
par(mfrow=c(2,1),mar=c(4,5,2,1), cex.lab=1.3, cex.axis=1.1, cex.main=1.4)
hist(normsamp,nclass=100,freq=F,main="Histogram with density curve",col=grey(0.8))

y <- seq(from=2,to=18,le=700)
lines(y,dnorm(y,mean = 10, sd=5),type="l",col="blue",lwd=2,xlab="",ylab="Density")

norm.mean <- rep(0,2000)
for (i in 1:2000){
  norm.subset <- sample(normsamp,size=3,replace=T)
  norm.mean[i] <- mean(norm.subset)
}

hist(norm.mean,nclass=100,freq=F,xlab="Sample mean",main="Sampling distribution of mean with n=3")
lines(density(norm.mean,bw=0.5),col="blue",lwd=2)
```

n=10 from normal distribution
```{r}
#Normal Distribution with N=10,000
#n=10
normsamp <- rnorm(10000,mean = 10, sd=5)
par(mfrow=c(2,1),mar=c(4,5,2,1), cex.lab=1.3, cex.axis=1.1, cex.main=1.4)
hist(normsamp,nclass=100,freq=F,main="Histogram with density curve",col=grey(0.8))

y <- seq(from=2,to=18,le=700)
lines(y,dnorm(y,mean = 10, sd=5),type="l",col="blue",lwd=2,xlab="",ylab="Density")

norm.mean <- rep(0,2000)
for (i in 1:2000){
  norm.subset <- sample(normsamp,size=10,replace=T)
  norm.mean[i] <- mean(norm.subset)
}

hist(norm.mean,nclass=100,freq=F,xlab="Sample mean",main="Sampling distribution of mean with n=10")
lines(density(norm.mean,bw=0.25),col="blue",lwd=2)
```

n=50 from normal distribution
```{r}
#Normal Distribution with N=10,000
#n=50
normsamp <- rnorm(10000,mean = 10, sd=5)
par(mfrow=c(2,1),mar=c(4,5,2,1), cex.lab=1.3, cex.axis=1.1, cex.main=1.4)
hist(normsamp,nclass=100,freq=F,main="Histogram with density curve",col=grey(0.8))

y <- seq(from=2,to=18,le=700)
lines(y,dnorm(y,mean = 10, sd=5),type="l",col="blue",lwd=2,xlab="",ylab="Density")

norm.mean <- rep(0,2000)
for (i in 1:2000){
  norm.subset <- sample(normsamp,size=50,replace=T)
  norm.mean[i] <- mean(norm.subset)
}

hist(norm.mean,nclass=100,freq=F,xlab="Sample mean",main="Sampling distribution of mean with n=50")
lines(density(norm.mean,bw=0.15),col="blue",lwd=2)
```

n = 100 from normal distribution
```{r}
#Normal Distribution with N=10,000
#n=100
normsamp <- rnorm(10000,mean = 10, sd=5)
par(mfrow=c(2,1),mar=c(4,5,2,1), cex.lab=1.3, cex.axis=1.1, cex.main=1.4)
hist(normsamp,nclass=100,freq=F,main="Histogram with density curve",col=grey(0.8))

y <- seq(from=2,to=18,le=700)
lines(y,dnorm(y,mean = 10, sd=5),type="l",col="blue",lwd=2,xlab="",ylab="Density")

norm.mean <- rep(0,2000)
for (i in 1:2000){
  norm.subset <- sample(normsamp,size=100,replace=T)
  norm.mean[i] <- mean(norm.subset)
}

hist(norm.mean,nclass=100,freq=F,xlab="Sample mean",main="Sampling distribution of mean with n=100")
lines(density(norm.mean,bw=0.1),col="blue",lwd=2)
```

n = 3 from exponential disitribution
```{r}
#Exponential Distribution with N=10,000
#n=3
expsamp <- rexp(10000,rate = 0.8)
par(mfrow=c(2,1),mar=c(4,5,2,1), cex.lab=1.3, cex.axis=1.1, cex.main=1.4)
hist(expsamp,nclass=100,freq=F,main="Histogram with density curve",col=grey(0.8))

y <- seq(from=0,to=18,le=700)
lines(y,dexp(y,rate=0.8),type="l",col="blue",lwd=2,xlab="",ylab="Density")

exp.mean <- rep(0,2000)
for (i in 1:2000){
  exp.subset <- sample(expsamp,size=3,replace=T)
  exp.mean[i] <- mean(exp.subset)
}

hist(exp.mean,nclass=100,freq=F,xlab="Sample mean",main="Sampling distribution of mean with n=3")
lines(density(exp.mean,bw=0.5),col="blue",lwd=2)

```

n = 10 from exponential distribution
```{r}
#Exponential Distribution with N=10,000
#n=10
expsamp <- rexp(10000,rate = 0.8)
par(mfrow=c(2,1),mar=c(4,5,2,1), cex.lab=1.3, cex.axis=1.1, cex.main=1.4)
hist(expsamp,nclass=100,freq=F,main="Histogram with density curve",col=grey(0.8))

y <- seq(from=0,to=18,le=700)
lines(y,dexp(y,rate=0.8),type="l",col="blue",lwd=2,xlab="",ylab="Density")

exp.mean <- rep(0,2000)
for (i in 1:2000){
  exp.subset <- sample(expsamp,size=10,replace=T)
  exp.mean[i] <- mean(exp.subset)
}

hist(exp.mean,nclass=100,freq=F,xlab="Sample mean",main="Sampling distribution of mean with n=10")
lines(density(exp.mean,bw=0.25),col="blue",lwd=2)
```

n = 50 from exponential distribution
```{r}
#Exponential Distribution with N=10,000
#n=3
expsamp <- rexp(10000,rate = 0.8)
par(mfrow=c(2,1),mar=c(4,5,2,1), cex.lab=1.3, cex.axis=1.1, cex.main=1.4)
hist(expsamp,nclass=100,freq=F,main="Histogram with density curve",col=grey(0.8))

y <- seq(from=0,to=18,le=700)
lines(y,dexp(y,rate=0.8),type="l",col="blue",lwd=2,xlab="",ylab="Density")

exp.mean <- rep(0,2000)
for (i in 1:2000){
  exp.subset <- sample(expsamp,size=50,replace=T)
  exp.mean[i] <- mean(exp.subset)
}

hist(exp.mean,nclass=100,freq=F,xlab="Sample mean",main="Sampling distribution of mean with n=50")
lines(density(exp.mean,bw=0.15),col="blue",lwd=2)
```

n = 100 from exponential distribution
```{r}
#Exponential Distribution with N=10,000
#n=3
expsamp <- rexp(10000,rate = 0.8)
par(mfrow=c(2,1),mar=c(4,5,2,1), cex.lab=1.3, cex.axis=1.1, cex.main=1.4)
hist(expsamp,nclass=100,freq=F,main="Histogram with density curve",col=grey(0.8))

y <- seq(from=0,to=18,le=700)
lines(y,dexp(y,rate=0.8),type="l",col="blue",lwd=2,xlab="",ylab="Density")

exp.mean <- rep(0,2000)
for (i in 1:2000){
  exp.subset <- sample(expsamp,size=100,replace=T)
  exp.mean[i] <- mean(exp.subset)
}

hist(exp.mean,nclass=100,freq=F,xlab="Sample mean",main="Sampling distribution of mean with n=100")
lines(density(exp.mean,bw=0.1),col="blue",lwd=2)
```

n = 3 from binomial distribution
```{r,warning=FALSE}
#Binomial Distribution with N=10,000
#n=3
x <- rbinom(n =  10000, 1,p = 0.1)
par(mfrow=c(2,1),mar=c(4,5,2,1), cex.lab=1.3, cex.axis=1.1, cex.main=1.4)
hist(x,freq=F,main="Histogram with density curve",col=grey(0.8))

y <- seq(from=0,to=1,le=20)
lines(y,dbinom(y,1,p=0.1),type="l",col="blue",lwd=2,xlab="",ylab="Density")

x.mean <- rep(0,2000)
for (i in 1:2000){
  x.subset <- sample(x,size=3,replace=T)
  x.mean[i] <- mean(x.subset)
}
hist(x.mean,nclass=7,freq=F,xlab="Sample mean",main="Sampling distribution of mean with n=3")
lines(density(x.mean,bw=0.15),col="blue",lwd=2)
```

n = 10 from binomial distribution
```{r,warning=FALSE}
#Binomial Distribution with N=10,000
#n=10
x <- rbinom(n =  10000, 1,p = 0.1)
par(mfrow=c(2,1),mar=c(4,5,2,1), cex.lab=1.3, cex.axis=1.1, cex.main=1.4)
hist(x,freq=F,main="Histogram with density curve",col=grey(0.8))

y <- seq(from=0,to=1,le=20)
lines(y,dbinom(y,1,p=0.1),type="l",col="blue",lwd=2,xlab="",ylab="Density")

x.mean <- rep(0,2000)
for (i in 1:2000){
  x.subset <- sample(x,size=10,replace=T)
  x.mean[i] <- mean(x.subset)
}
hist(x.mean,nclass=7,freq=F,xlab="Sample mean",main="Sampling distribution of mean with n=10")
lines(density(x.mean,bw=0.1),col="blue",lwd=2)
```

n = 50 from binomial distribution
```{r,warning=FALSE}
#Binomial Distribution with N=10,000
#n=50
x <- rbinom(n =  10000, 1,p = 0.1)
par(mfrow=c(2,1),mar=c(4,5,2,1), cex.lab=1.3, cex.axis=1.1, cex.main=1.4)
hist(x,freq=F,main="Histogram with density curve",col=grey(0.8))

y <- seq(from=0,to=1,le=20)
lines(y,dbinom(y,1,p=0.1),type="l",col="blue",lwd=2,xlab="",ylab="Density")

x.mean <- rep(0,2000)
for (i in 1:2000){
  x.subset <- sample(x,size=50,replace=T)
  x.mean[i] <- mean(x.subset)
}
hist(x.mean,nclass=7,freq=F,xlab="Sample mean",main="Sampling distribution of mean with n=50")
lines(density(x.mean,bw=0.05),col="blue",lwd=2)
```

n = 100 from binomial distribution
```{r,warning=FALSE}
#Binomial Distribution with N=10,000
#n=100
x <- rbinom(n =  10000, 1,p = 0.1)
par(mfrow=c(2,1),mar=c(4,5,2,1), cex.lab=1.3, cex.axis=1.1, cex.main=1.4)
hist(x,freq=F,main="Histogram with density curve",col=grey(0.8))

y <- seq(from=0,to=1,le=20)
lines(y,dbinom(y,1,p=0.1),type="l",col="blue",lwd=2,xlab="",ylab="Density")

x.mean <- rep(0,2000)
for (i in 1:2000){
  x.subset <- sample(x,size=100,replace=T)
  x.mean[i] <- mean(x.subset)
}
hist(x.mean,nclass=7,freq=F,xlab="Sample mean",main="Sampling distribution of mean with n=100")
lines(density(x.mean,bw=0.05),col="blue",lwd=2)
```

